new_analses

### 2021-07-13 new_analyses.Rmd
lkl

```{r}
library(tidyverse)
library(lubridate)
library(drc)
library(broom)
library(tidytext)
library(ggthemes)
library(ggtext)
```

@@

```{r}
data1 %>% 
  mutate(month = fct_recode(month,
                            "First transplanting" = "June",
                            "Second transplanting" = "July")) -> data1
```

>>>>

```{r}
library(tidyverse)
library(lubridate)
library(drc)
library(broom)
library(tidytext)
library(ggthemes)
library(ggtext)
library(patchwork)
library(extrafont)
library(showtext)
showtext_auto()
font_add_google("Roboto", "roboto") 
```

@@

```{r}
data1 %>% 
  mutate(month = fct_recode(month,
                            "First transplanting" = "June",
                            "Second transplanting" = "July")) -> data1
```
```{r}
data1 %>% 
  filter(!is.na(weight)) %>% 
  group_by(year, location, month, crop) %>% 
  mutate(n = n()) %>% 
  mutate(biomass = weight / n) -> biom
```
```{r}
biom %>% 
  ggplot(aes(x = log(biomass))) + 
  geom_histogram()
```

```{r}
library(lme4)
library(lmerTest)
library(emmeans)
```

```{r}
biom %>%
  group_by(month) %>% 
  nest(-month) %>% 
  mutate(model = map(data, ~ lmer(log(biomass) ~ crop * location + 
                                 (1|year), data = .x)),
         anova = map(model, anova),
         emmeans = map(model, ~ emmeans(., ~ location | crop, 
                                        type = "response"))) -> analysis
```

```{r}
#anova
analysis$anova[[2]]
```

```{r}
analysis$emmeans[[2]] %>% 
  as_tibble() %>% 
  mutate(month = "Second transplanting") -> second

analysis$emmeans[[1]] %>% 
  as_tibble() %>% 
  mutate(month = "First transplanting") %>% 
  bind_rows(second) %>% 
  mutate(location = str_to_title(location)) %>% 
  mutate(location = fct_recode(location,
                              "Lincoln" = "Havelock")) -> result
```

```{r}
result %>% 
  filter(month == "First transplanting") %>% 
  group_by(month, crop) %>% 
  mutate(location = reorder_within(location, 
                                   by = response, 
                                   within = crop)) %>% 
  ggplot(aes(x = location, y = response,
             color = location)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.CL, ymax = upper.CL)) +
  scale_color_manual(values = c(1,2,4,3,5, 1,3,2,4,5, 1,2,4,3,5)) +
  facet_grid(crop ~ month, scales = "free") +
  coord_flip() +
  ylim(0, 30) +
  scale_x_reordered() +
  labs(y = expression(paste("Biomass (g plant "^"-1",")")), x = NULL) +
  theme_test() +
  theme(legend.position = "none") -> first

ggsave("first.png", width = 3)
```

```{r}
theme_set(theme_test(base_family = "roboto"))
result %>% 
  filter(month == "Second transplanting") %>% 
  group_by(month, crop) %>% 
  mutate(location = reorder_within(location, 
                                   by = response, 
                                   within = crop)) %>% 
  ggplot(aes(x = location, y = response,
             color = location)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.CL, ymax = upper.CL)) +
  scale_color_manual(values = c(1,2,3,4,5, 1,4,2,3,5, 1,2,3,4,5)) +
  facet_grid(crop ~ month, scales = "free") +
  coord_flip() +
  ylim(0, 80) +
  scale_x_reordered() +
  labs(y = expression(paste("Biomass (g plant "^"-1",")")), x = NULL) +
  theme_test() +
  theme(legend.position = "none") -> second

ggsave("second.png", width = 3)
```

```{r}
first | second

ggsave("biomass.png", width = 6)
```

```{r}
biom %>% 
  ggplot(aes(x = crop, y = biomass, label = n)) +
  geom_jitter(alpha = 0.2) +
  geom_boxplot() +
  facet_grid(~month, scales = "free") +
  coord_flip()
```

```{r}
data1 %>% 
  ggplot(aes(x = crop, y = weight)) +
  geom_jitter(alpha = 0.2) +
  facet_grid(month ~ location) +
  coord_flip()
```
